---
title: "Replication Log for Foster (2023) Subject to Change"
author: "Margaret J. Foster"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
```

## Introduction

This document produces a replication log for the tables and figures made in R for Subject to Change: Quantifying Transformation in Armed Conflict Actors At Scale Using Text. STATA-produced tables are featured in accompanying scripts.

These results are generated from an R data file that was produced as part of the research, 01measurementScaleUpInProgressTiny55.Rdata.
Replication code to produce the data can be found in the "01measurementFullDataTinyThreshRep.R" R script. 
Another data file, 02dfyearsumAndRelatedTinyUpdate.Rdata, is produced by "02tinyThreshTransformVarRep.R" in the replication package.


## Manuscript and Appendix Figure 1
```{r Figs1, echo=FALSE}
rm(list=ls())

## load packages to clean and work with data
library(ggplot2)
library(ggridges)
library(tidyverse)
library(readxl)
library(stargazer)
library(stringi)

outPath <- "./"

load(file=paste0(outPath,
         "02dfyearsumAndRelatedTinyUpdate.Rdata"))

##%%%%%%%%%%%%%%%%%%%%%%%%%%%
### Data + Summary Stats
## Subset with a minimum threshold of 10 events (and 10 words to model)
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### Plot summaries of number of violent events
## Associated with each group
## Table of the data:

freqs <- as.data.frame(table(df.basedata$side_b_new_id))

## Add names:
freqs <- merge(x=freqs,
               y=unique(df.basedata[,
                   c("side_b_new_id", "side_b")]),
               by.y="side_b_new_id",
               by.x="Var1",
               all.x=TRUE)

freqs <- freqs[order(freqs$Freq),]

freqs$quartile <- NA
freqs[which(freqs$Freq <= 25), "quartile"] <- "First"
freqs[which(freqs$Freq > 25 &
            freqs$Freq <= 75), "quartile"] <- "Second"
freqs[which(freqs$Freq > 75 &
            freqs$Freq <= 219), "quartile"] <- "Third"
freqs[which(freqs$Freq > 219), "quartile"] <- "Fourth"

## Min: 10, max 60814;
## Median: 75
## Merge the quartile variable back into the basedata:
## and yearly data

df.basedata <- merge(x=df.basedata,
                     y=freqs,
                     by.x= c("side_b_new_id", "side_b"),
                     by.y=c("Var1", "side_b"))

df.yearsum2 <- merge(x=df.yearsum,
                     y=freqs,
                     by.x= c("groupID"),
                     by.y=c("Var1"))

## Change name for readability
colnames(df.basedata)[which(
    colnames(df.basedata)=="Freq")] <- "GroupNumEvents"

## Graph the length of the news articles.
## Want to check for systematic differences across
## the set of groups. In this case, ruling out difference
##  by activity level:
  
df.basedata$nwords <- stringi::stri_count_words(
    df.basedata$source_article)

##%%%%%%%%%%%%%
## Appendix Figure One
##%%%%%%%%%%%%%%%
##
df.basedata$quartile <- as.factor(df.basedata$quartile)
df.basedata$quartile <- factor(df.basedata$quartile,
                              levels = c("First", "Second",
                                  "Third", "Fourth"))

df.basedata$side_b[grep(as.character(df.basedata$side_b),
                        pattern="Consolidation")] <- "Military Junta CDPJ"



########################
## Make an overview of groups that change
## and "oscillating" groups, so that you can
## cross-reference these groups with UCDP encyclopedia

## want to count propdiff L1 and tally the number that are:
## (a) greater than = |1|
## (b) Between |1| and |1.5|
## (c) between |1.5| and |2|
## (d) equal to |2|

df.yearsum.plot <- df.yearsum2 %>%
    filter(!is.na(propdif.L1))

df.yearsum.plot$quartile <- factor(df.yearsum.plot$quartile,
                              levels = c("First", "Second",
                                  "Third", "Fourth"))

## subset to groups with more than 5 articles modeled:
active.year.freqs <-  as.data.frame(table(
    df.yearsum.plot$groupID))

active.year.freqs <- active.year.freqs[order(
    active.year.freqs$Freq),]

freqs.g3 <- active.year.freqs[which(
    active.year.freqs$Freq >= 3),]

freqs.g5 <- active.year.freqs[which(
    active.year.freqs$Freq >= 5),]

df.yearsum.plot$side_b[grep(
    as.character(df.yearsum.plot$side_b),
    pattern="Consolidation")] <- "Military Junta CDPJ"

## Three active-year threshold
ggdata <- df.yearsum.plot[which(df.yearsum.plot$groupID
                                %in% freqs.g3$Var1),]

####################
## Manuscript Figure One:
######################

gch <- ggplot(ggdata,
             aes(x=propdif.L1,
                    y=side_b,
                 group = side_b)) +
    geom_density_ridges2()+
    scale_y_discrete(limits=rev)+
    labs(x= "Distribution of Yearly Proportion Changes",
           y="Actor")+
    ggtitle(label="Overview of Yearly Proportion Changes",
            subtitle="Grouped By Quartiles of Activity Level")+
    theme_bw()+
   facet_wrap(~quartile, scales="free")+
    theme(axis.text.y=element_text(size=3))

gch ## Manuscript Figure One

####
## Appendix Figure One
##
gr <- ggplot(df.basedata,
             aes(x=nwords,
                    y=side_b,
                 group = side_b)) +
    geom_density_ridges2()+
    scale_x_log10() +
    scale_y_discrete(limits=rev)+
    labs(x= "Distribution of Words in Source Articles",
           y="UCDP Actor")+
    ggtitle(label="Distribution of Article Lengths",
            subtitle="Grouped By Quartiles of Activity Level")+
    theme_bw()+
    facet_wrap(~quartile, scales="free")+
    theme(axis.text.y=element_text(size=3))

gr ## Appendix Figure One
##ggsave(gr,
##       file="distArticleLengthsTiny.pdf")

```

## Manuscript Table One and Appendix Figures 11 and 12
The following code prepares the data generated by the Subject To Change measurement for replication of Nilsson and Svensson (2021).
The replication log for the Termination and Recurrence models are in the accompanying Stata Markdown output.

The code chunk also produces:
- Appendix Figure 11, the correlation plot heatmap for change and ambiguity variables.
- Article Figure 2 and Appendix Figure 12, which are summaries of the distribution of the new change variables.

```{r repdata, echo=FALSE}

rm(list=ls())

library(tidyverse)
library(haven)
library(dplyr)
library(corrplot)
library(stargazer)

dataPath <- "./"

## Read in Nilsson and Svenson's data:
termination <- read_dta(paste0(dataPath,
                               "Termination-data-ISQ.dta"))

changes <- load("./02dfyearsumAndRelatedTinyUpdate.Rdata")

idkey <- read_csv(paste0(dataPath,"translate_actor.csv"))

## Add the new/old ID key:
t.groups.after1989 <- unique(termination[which(
    termination$year>=1989),]$sidebid)

c.groups <- unique(df.yearsum$groupID)

## Match group IDs:. 
## Nilsson and Svensson based their work on:
## UCDP Conflict Termination Dataset version 2–2015, which is before
## UCDP changed the id numbering scheme.

termination$sidebid <- as.numeric(termination$sidebid)
ids.termination <- unique(termination$sidebid)

termination <- merge(termination,
                     idkey,
                     by.x=("sidebid"),
                     by.y=("old_id"),
                     all.x=TRUE)

ids.yearsum <- unique(df.yearsum$groupID)
terminationplus1 <- merge(x=termination,
                         y=df.yearsum,
                         by.x=c("new_id", "year"),
                         by.y=c("groupID", "year"),
                         all.x=TRUE)

## Terminationplus1 is more or less their original data
## limit to 1989 and later

terminationplus <- terminationplus1[which(
    terminationplus1$year>=1989),]

## Identify the armed groups that had a change of
## 1, 1.5 and greater than 2:

haddelta1 <- unique(terminationplus[which(
    terminationplus$delta1==1),]$new_id)

haddelta1.5 <- unique(terminationplus[which(
    terminationplus$delta1.5==1),]$new_id)

haddelta2 <- unique(terminationplus[which(
    terminationplus$delta2==1),]$new_id)

## Add in the indicator variable for whether
## the militant group in a dyad had a change
## In any year:

terminationplus$haddelta1 <- 0
terminationplus$haddelta1 <- ifelse(terminationplus$new_id
                                    %in% haddelta1, 1, 0)

terminationplus$haddelta1.5 <- 0
terminationplus$haddelta1.5 <- ifelse(terminationplus$new_id
                                    %in% haddelta1.5, 1, 0)
terminationplus$haddelta2 <- 0
terminationplus$haddelta2 <- ifelse(terminationplus$new_id
                                    %in% haddelta2, 1, 0)

numchanges<- terminationplus %>%
    group_by(new_id) %>%
    summarise(numchanges=sum(delta1==1))

## merge back in:
terminationplus <- terminationplus %>%
    left_join(numchanges,
              by="new_id") 

##%%%%%%%%%%%%%%%%%
## Summary statistics
## For change and also for the introduced variables
##%%%%%%%%%%%%%%%%%%
## number of changes
## Count variable

## format a small DF to report summary statistics:
## for the binary variables:

binaries <- c("Change year",
              "Change in Prev. 2 years",
              "Had 'Low' Change",
              "Had 'Med.' Change",
              "Had 'High' Change")

df <- as.data.frame(cbind(binaries,
                          rbind(table(terminationplus$delta1),
                                table(terminationplus$delta1_L2),
                                table(terminationplus$haddelta1),
                                table(terminationplus$haddelta1.5),
                                table(terminationplus$haddelta2))))

print(table(terminationplus$delta1))
table(terminationplus$delta1_L2)


## Article Figure 2:
#colnames(df) <- c("Variable", "No", "Yes")
stargazer(df, summary=FALSE, rownames=FALSE)


sum.df <- terminationplus[,c("numchanges","counter")]

## Appendix Figure 12:
stargazer(sum.df,
          covariate.labels =c("Number of Changes",
              "Years Since Change"
              ))

##%%%%%%%%%%%%%%%%%%%%%
## Save and format for STATA
## (aka: remove periods from the column names)

colnames(terminationplus)[which(
    colnames(terminationplus)=="propdif.L1")] <- "propdif_L1"
colnames(terminationplus)[which(
    colnames(terminationplus)=="propdif.L2")] <- "propdif_L2"
colnames(terminationplus)[which(
    colnames(terminationplus)=="altpropdif.L1")] <- "altpropdif_L1"
colnames(terminationplus)[which(
    colnames(terminationplus)=="altpropdiff.L1")] <- "altpropdiff_L1"
colnames(terminationplus)[which(
    colnames(terminationplus)=="delta1.5")] <-"delta15"
colnames(terminationplus)[which(
    colnames(terminationplus)=="haddelta1.5")] <-"haddelta15"

## Pass out data
##write_dta(data=terminationplus,
##          "./terminationplus.dta")

##%%%%%%%%%%%%%%%%%%%%%%%
## Make correlation plots:
##%%%%%%%%%%%%%%%%%%%%%%

tocompare <- c("haddelta1",
               "haddelta1_5",
               "haddelta2",
               "transstart", ## 169 NA
               "islamist", "muslimid",
               "rebextpartdummy", ## 182 NA
               "strongstart", ##92 NA
               "forinvstart",
               "muslimajstart",
               "oilstart", ## 37 NA
               "duration" ,
               "lngdppc", ## 33 NA
               "lnpop",## 33 NA
               "youthstartap", ##112 NA
               "foreignfighter",
               "number_group",
               "secsup_govgov", ## 102 NA
               "anostart" , ## 96 na
               "anocracy", ## 39 NA
               "rebv",
               "lowcease",
               "territory" ,
               "pa", "ca","govv",
               ## "outcome",  ## 800 plus NA, distorts data avali.
               "intensitylevel")
 
term.mod.vars <- c("term",# ""Termination"
              "islamist",# "Islamist claim"
              "haddelta1",# "Had Change |1|"
              "haddelta15",# "Had Change |1.5|"
              "haddelta2",# "Had Change |2|"
              "territory",# "Territory"
              "duration",# "Duration"
              "intensitylevel",# "War"
              "number_group",# "Number of groups"
              "strongstart",# "Strong rebels"
              "anostart",# "Anocracy"
              "lngdppcstart",# "GDP per capita"
              "lnpopstart",# "Population"
              "muslimajstart",# "Muslim majority"
              "oilstart",# "Oil"
              "youthstartap",# "Youth bulge/adult pop."
              "anocracy",# "Anocracy over time"
              "lngdppc",# "GDP per capita over time"
              "lnpop",# "Population over time"
              "foreignfighter",# "Foreign fighters"
              "govmilsupport",# "Government support"
              "leftist",# "Leftist"
              "nonislamistrel",# "Non-Islamist religious claims"
              "muslimid",# "Muslim identity"
              "secsup_govgov",# "Government secondary support"
              "rebextpartdummy")# "Rebel support"

## Names:
term.mod.names <- c("Termination",
                    "Islamist claim",
                    "Had Change |1|",
                    "Had Change |1.5|",
                    "Had Change |2|",
                    "Territory",
                    "Duration",
                    "War",
                    "Number of groups",
                    "Strong rebels",
                    "Anocracy",
                    "GDP per capita",
                    "Population",
                    "Muslim majority",
                    "Oil",
                    "Youth bulge",
                    "Anocracy",
                    "GDP p.c.",
                    "Population",
                    "Foreign fighters",
                    "Gvt support",
                    "Leftist",
                    "Non-I. Rel. claims",
                    "Muslim identity",
                    "Gvt sec. support",
                    "Rebel support") 

datsubset <- terminationplus[,term.mod.vars]
colnames(datsubset) <- term.mod.names

corrmod2 <- cor(datsubset,
                use="complete.obs")

## Note: Hand crop b/c corrplot prints with huge margins
## pdf(file="correlationPlotTermVars.pdf")
corrplot(corrmod2,
         method="shade",
        ## type="lower",
         order="hclust",
         tl.cex = .8,
         tl.col="black",
         addrect=2,
         mar=c(1,1,1,1))
##dev.off()
 
##save(terminationplus, termination,
##     file="terminationPlusforRep.Rdata")

print("Finished making figures; Formatting data for STATA")
```

## Group Change-Year Plots
The following code replicates the group-year summary plots. 
These are Appendix Figures 2 (AQAP), 3 (Abu Sayyaf), 4 (ULFA), 5 (LRA), and Appendix Figure 10a (PKK)

```{r groupPlots, echo=FALSE}
rm(list=ls())

library(ggplot2)
library(tidyverse)
library(stargazer)
library(ggrepel)

load(file="./02dfyearsumAndRelatedTinyUpdate.Rdata")

##Which groups had a delta of at least |1|:
haddelta1 <- df.yearsum[which(
    abs(df.yearsum$propdif.L1) >= 1),]

c.groups <- unique(haddelta1$groupID) ## change groups
a.groups <- unique(df.yearsum$groupID) ## all groups

groups.nochange <- setdiff(a.groups,c.groups)

subset <- df.yearsum[which(
    df.yearsum$groupID %in% groups.nochange),]

## Hamas framing: 
## Footnote 7 in the text:
print(subset[which(subset$groupID==209),
            c("year", "frexWords")], n=32)

#####################
## Plots
#####################
## AQAP Case
aqap.sub <- df.basedata[which(
    df.basedata$side_b_dset_id==881),]

#dim(aqap.sub) ## 916 x 53

aqap.sub.year <- df.yearsum[which(
    df.yearsum$groupID == 881), ]

t1 <- unique(aqap.sub.year[which(
    aqap.sub.year$propT1>.75),]$frexWords)

t2 <- unique(aqap.sub.year[which(
    aqap.sub.year$propT2>.75),]$frexWords)

## Ggplot version:

textanchor <- min(aqap.sub$year)+5
num.articles <- dim(aqap.sub)[1]
x.breaks <- min(unique(aqap.sub$year)):max(unique(aqap.sub$year))

## highlight examples of stories before and after:
## The following code identifies articles
## The text is often messy, so the code extracts neatly formatted keywords

cols <- c("id", "source_article",
          "year", "maxtopic","scaledvalue")
## want to highlight on both sides of the 2015 switch:

t1.neg75 <- c("Al-Qaida kills 6 captured Yemeni rebels \n north of Aden")
t2.75 <- c("'Qaeda' ambush kills 5 Yemen soldiers")

## Make the subset and annotation columns:

aqap.sub$highlight <- 0
aqap.sub$caption <- ''

aqap.sub[which(aqap.sub$id==203501), "highlight"] <- 1
aqap.sub[which(aqap.sub$id==203501), "caption"] <- t2.75
aqap.sub[which(aqap.sub$id==205671), "highlight"] <- 1
aqap.sub[which(aqap.sub$id==205671), "caption"] <- t1.neg75

aqap.sub[which(aqap.sub$id==718), "highlight"] <- 1
aqap.sub[which(aqap.sub$id==718), "caption"] <- "Qaeda suspect kills two guards in Yemen hospital escape bid"

aqap.sub[which(aqap.sub$id==220), "highlight"] <- 1
aqap.sub[which(aqap.sub$id==220), "caption"] <- "Yemeni security forces said on alert for Qa'idah attacks in south"

aqap.sub[which(aqap.sub$id==367164), "highlight"] <- 1
aqap.sub[which(aqap.sub$id==367164), "caption"] <- "Al-Qaeda in Yemen claims attacks on Houthis despite defeat proclamation"


## Directly annotate the stories on the plot:

textanchor <- min(aqap.sub$year)+3

p.aqap2 <-ggplot(aqap.sub, aes(x=year, y=scaledvalue))+
    geom_jitter(width = 0.1, height = 0.1, alpha=.35)+
    geom_hline(yintercept=0, size=.75,
               color="red", alpha=.5) +
    geom_line(data=aqap.sub.year, aes(y=propdiff, x=year),
              color="darkgreen", linetype="dashed")+
    geom_label_repel(box.padding = 0.5,
                     max.overlaps = Inf,
                     data=as.data.frame(
                         aqap.sub[which(aqap.sub$highlight==1),]),
                     aes(label=caption))+
    geom_point(data=as.data.frame(
                   aqap.sub[which(aqap.sub$highlight==1),]),
               color = "red")+
    annotate("text", x = textanchor, y =1.15,
             label = paste0("Topic Two: ", t2))+
    annotate("text", x =textanchor, y = -1.15,
             label = paste0("Topic One: ", t1)) +
    xlab("Year")+
    scale_x_continuous(breaks=x.breaks,
                   guide = guide_axis(n.dodge = 2))+
    ylab("Proportion Topic 1 (-1) vs Topic 2 (1)") +
    ggtitle("AQAP Yearly Classification",
            subtitle=paste0("N = ", num.articles," Articles"))+
    theme_bw()

p.aqap2

ggsave(p.aqap2,
       width=12, 
       height=8,
       units=c("in"),
       file="annotedAQAPGraph.pdf")

#############
## Abu Sayyaf
############

as.sub <- df.basedata[which(
    df.basedata$side_b_dset_id==277),]
as.sub.year <- df.yearsum[which(
    df.yearsum$groupID == 277), ]
as.sub.year


## FREX Words to overlay
t1 <- unique(as.sub.year[which(
    as.sub.year$propT1>.75),]$frexWords)

t2 <- unique(as.sub.year[which(
    as.sub.year$propT2>.75),]$frexWords)

textanchor <- max(as.sub$year)-10
num.articles <- dim(as.sub)[1]
x.breaks <- min(unique(as.sub$year)):max(unique(as.sub$year))

cols <- c("id","source_article",
          "year", "maxtopic","scaledvalue")

## Build in the highlighted articles
## in a way that is efficient for ggplot:
as.sub$highlight <- 0
as.sub$caption <- ''

## Captions:

as.sub[which(as.sub$id== 124923),
       "highlight"] <- 1
as.sub[which(as.sub$id==124923),
       "caption"] <- "Six Abu Sayyaf fighters, two soldiers dead in clash"

as.sub[which(as.sub$id==123716),
       "highlight"] <- 1
as.sub[which(as.sub$id==123716),
       "caption"] <- "Philippines foils rebel bid to escape hostage isle"

as.sub[as.sub$id==298896, "caption"] <- "IS claims killing soldier in southern Philippines"
as.sub[as.sub$id==298896, "highlight"] <- 1

as.sub[which(as.sub$id== 203613),
       "highlight"] <- 1
as.sub[which(as.sub$id==203613),
       "caption"] <- "Al-Qaeda-linked militants behead Philippine militiaman"


textanchor <- max(as.sub$year)-10
num.articles <- dim(as.sub)[1]
x.breaks <- min(unique(as.sub$year)):max(unique(as.sub$year))

p.as2 <-ggplot(as.data.frame(as.sub),
               aes(x = year, y = scaledvalue))+
    geom_jitter(width = 0.1, height = 0.1, alpha=.35)+
    geom_label_repel(box.padding = 0.5,
                    max.overlaps = Inf,
                    data=as.data.frame(
                        as.sub[which(as.sub$highlight==1),]),
                    aes(label=caption))+
    geom_point(data=as.data.frame(
                   as.sub[which(as.sub$highlight==1),]),
               color = "red")+
    geom_hline(yintercept=0, size=.75,
                   color="red", alpha=.5) +
    geom_line(data=as.sub.year, aes(y=propdiff, x=year),
              color="darkgreen", linetype="dashed")+
    xlab("Year")+
    scale_x_continuous(breaks=x.breaks,
                   guide = guide_axis(n.dodge = 2))+
    ylab("Proportion Topic 1 (-1) vs Topic 2 (1)") +
    ggtitle("Abu Sayyaf Yearly Classification",
            subtitle=paste0("N = ", num.articles," Articles"))+
    theme_bw()

p.as2

ggsave(p.as2,
       width=12, 
       height=8,
       units=c("in"),
       file="annotedAbuSayyaf.pdf")

#############
## ULFA
############

ulfa.sub <- df.basedata[which(
    df.basedata$side_b_dset_id==326),]
ulfa.sub.year <- df.yearsum[which(
    df.yearsum$groupID == 326), ]


## Articles to highlight;

ulfa.sub$highlight <- 0
ulfa.sub$caption <- ''

ulfa.sub[which(ulfa.sub$id==94984),"highlight"]  <- 1
ulfa.sub[which(ulfa.sub$id==94984), "caption"] <- "TWO KILLED AS INDIAN TROOPS HUNT FOR GUERRILLAS IN ASSAM"

ulfa.sub[which(ulfa.sub$id==95258), "highlight"] <- 1
ulfa.sub[which(ulfa.sub$id==95258), "caption"] <- "Indian troops kill 12 rebels in troubled northeast"

ulfa.sub[which(ulfa.sub$id==94990), "highlight"] <- 1
ulfa.sub[which(ulfa.sub$id==94990), "caption"] <- "TWO POLICEMEN KILLED BY SUSPECTED ASSAM MILITANTS"

ulfa.sub[which(ulfa.sub$id==95275), "highlight"] <- 1
ulfa.sub[which(ulfa.sub$id==95275), "caption"] <- "One killed, seven wounded in grenade attack in northeast India"

ulfa.sub[which(ulfa.sub$id==95084), "highlight"] <- 1
ulfa.sub[which(ulfa.sub$id==95084), "caption"] <- "Five policemen, civilian killed in Assam ambush"

ulfa.sub[which(ulfa.sub$id==156739), "highlight"] <- 1
ulfa.sub[which(ulfa.sub$id==156739), "caption"] <- "Trader shot dead in Kokrajhar"

ulfa.sub[which(ulfa.sub$id==67177), "highlight"] <- 1
ulfa.sub[which(ulfa.sub$id==67177), "caption"] <- "ULFA militant killed, arms recovered"

## FREX Words to overlay
t1 <- unique(ulfa.sub.year[which(
    ulfa.sub.year$propT1>.75),]$frexWords)

t2 <- unique(ulfa.sub.year[which(
    ulfa.sub.year$propT2>.75),]$frexWords)

textanchor <- max(ulfa.sub$year)-10
num.articles <- dim(ulfa.sub)[1]
x.breaks <- min(unique(ulfa.sub$year)):max(unique(ulfa.sub$year))

## Anotated graph

textanchor <- max(ulfa.sub$year)-10
num.articles <- dim(ulfa.sub)[1]
x.breaks <- min(unique(ulfa.sub$year)):max(unique(ulfa.sub$year))

p.ulfa2 <-ggplot(as.data.frame(ulfa.sub),
               aes(x = year, y = scaledvalue))+
    geom_jitter(width = 0.1, height = 0.1, alpha=.35)+
    geom_label_repel(box.padding = 0.5,
                    max.overlaps = Inf,
                    data=as.data.frame(
                        ulfa.sub[which(ulfa.sub$highlight==1),]),
                    aes(label=caption))+
    geom_point(data=as.data.frame(
                   ulfa.sub[which(ulfa.sub$highlight==1),]),
               color = "red")+
    geom_hline(yintercept=0, size=.75,
                   color="red", alpha=.5) +
    geom_line(data=ulfa.sub.year, aes(y=propdiff, x=year),
              color="darkgreen", linetype="dashed")+
    xlab("Year")+
    scale_x_continuous(breaks=x.breaks,
                   guide = guide_axis(n.dodge = 2))+
    ylab("Proportion Topic 1 (-1) vs Topic 2 (1)") +
    ggtitle("UFLA Yearly Classification",
            subtitle=paste0("N = ", num.articles," Articles"))+
    theme_bw()

p.ulfa2 

ggsave(p.ulfa2,
       width=12, 
       height=8,
       units=c("in"),
       file="annotedulfa.pdf")


#############
## LRA
############

lra.sub <- df.basedata[which(
    df.basedata$side_b_dset_id==488),]
lra.sub.year <- df.yearsum[which(
    df.yearsum$groupID == 488), ]


t1 <- unique(lra.sub.year[which(
    lra.sub.year$propT1>.75),]$frexWords)

t2 <-c("london,kill,rebel,africa,armi,new,vision")

textanchor <- max(lra.sub$year)-10
num.articles <- dim(lra.sub)[1]
x.breaks <- min(unique(lra.sub$year)):max(unique(lra.sub$year))

## Annotate

lra.sub$caption <- ''
lra.sub$highlight <- 0
 
## Pull some articles to illustrate:             
##lra.sub[which(lra.sub$year==1990 & 
##             lra.sub$scaledvalue <= .5), cols]

##lra.sub[which(lra.sub$year==2009 & 
##             lra.sub$scaledvalue > .25), cols]

##lra.sub[which(lra.sub$year==2017 & 
##              lra.sub$scaledvalue <= .5), cols]

lra.sub[which(lra.sub$id==36752), "highlight"] <- 1
lra.sub[which(lra.sub$id==36752), "caption"] <- "UGANDAN REBELS KILL 20 PEOPLE"

lra.sub[which(lra.sub$id==239443), "highlight"] <- 1
lra.sub[which(lra.sub$id==239443), "caption"] <- "Uganda LRA rebels kill 'scores' in northern DR Congo"

lra.sub[which(lra.sub$id==37656), "highlight"] <- 1
lra.sub[which(lra.sub$id==37656), "caption"] <- "The Wizard of the Nile [The Hunt for Joseph Kony]"


p.lra2 <-ggplot(as.data.frame(lra.sub),
               aes(x = year, y = scaledvalue))+
    geom_jitter(width = 0.1, height = 0.1, alpha=.35)+
    geom_label_repel(size=2.5,
      box.padding = .5,
                    max.overlaps = Inf,
                     data=as.data.frame(
                        lra.sub[which(lra.sub$highlight==1),]),
                    aes(label=caption))+
    geom_point(data=as.data.frame(
                   lra.sub[which(lra.sub$highlight==1),]),
               color = "red")+
    geom_hline(yintercept=0, size=.75,
                   color="red", alpha=.5) +
    geom_line(data=lra.sub.year, aes(y=propdiff, x=year),
              color="darkgreen", linetype="dashed")+
    xlab("Year")+
  ylim(-1, 1)+
    scale_x_continuous(breaks=x.breaks,
                   guide = guide_axis(n.dodge = 2))+
    ylab("Proportion Topic 1 (-1) vs Topic 2 (1)") +
    ggtitle("LRA Yearly Classification",
            subtitle=paste0("N = ", num.articles," Articles"))+
    theme_bw()

p.lra2

ggsave(p.lra2,
       width=12, 
       height=8,
       units=c("in"),
       file="annotedLRA.pdf")

##############################
## PKK
#############################
pkk.sub <- df.basedata[which(
    df.basedata$side_b_dset_id==323),]
pkk.sub.year <- df.yearsum[which(
    df.yearsum$groupID == 323), ]

## FREX Words to overlay
t1 <- unique(pkk.sub.year[which(
    pkk.sub.year$propT1>.75),]$frexWords)

t2 <- unique(pkk.sub.year[which(
    pkk.sub.year$propT2>.75),]$frexWords)

## Plot

textanchor <- max(pkk.sub$year)-10
num.articles <- dim(pkk.sub)[1]
x.breaks <- min(unique(pkk.sub$year)):max(unique(pkk.sub$year))

p.pkk <-ggplot(pkk.sub, aes(x=year, y=scaledvalue))+
    geom_jitter(width = 0.1, height = 0.1, alpha=.35)+
    geom_hline(yintercept=0, size=.75,
               color="red", alpha=.5) +
    geom_line(data=pkk.sub.year, aes(y=propdiff, x=year),
              color="darkgreen", linetype="dashed")+
    annotate("text", x = textanchor, y =1.15, label = t2)+
    annotate("text", x =textanchor, y = -1.15, label = t1) +
    xlab("Year")+
    scale_x_continuous(breaks=x.breaks,
                   guide = guide_axis(n.dodge = 2))+
    ylab("Proportion Topic 1 (-1) vs Topic 2 (1)") +
    ggtitle("PKK Yearly Classification",
            subtitle=paste0("N = ", num.articles," Articles"))+
    theme_bw()
p.pkk

#ggsave(p.pkk, file="PKKYearPlots.pdf")

```


## Precision and Media Access Figures
The following code produces Appendix Figures 6 and 7, which evaluate the effect of media access on estimated change points.

These snippets address whether the approach is more likely to find changes in difficult reporting environments, which would suggest that what is being modeled is something other than behavioral changes.


```{r pressure, echo=FALSE, warnings=FALSE}
rm(list=ls())

library(ggplot2)
library(tidyverse)
library(readxl)
library(countrycode)
library(sandwich)
library(lmtest)
library(plm)
library(pscl)
library(broom)

outPath <- "./"

load(file=paste0(outPath,
         "02dfyearsumAndRelatedTinyUpdate.Rdata"))


## Convert from country-year to group-year
## Idea: go into the df.basedata and merge in FH indicators
## for the country and year that the event happened in
## then take a per-group average?
## Need year events x country and country scores

df.basedata <- rename(df.basedata,
                      groupID = side_b_new_id)

df.precision <- df.basedata %>%
    group_by(groupID, year, country_id) %>%
     summarise(
         mean.time.prec= mean(date_prec),
         mean.loc.prec = mean(where_prec),
         mean.clarity = mean(event_clarity)
         )

## Add in the country code:
## via ccodes library

df.precision$cow <- countrycode(df.precision$country_id,
                                origin = "gwn",
                                destination = "cowc")

## Data source for journalism access
## Goddes and Cary (2021 and 2017) dataset on journalist murders
## They also us Freedom House Measures on media restrictions
## (Presumably in their replication data)
## & V-Dem's  Freedom of Expression and Alternative Sources of Information Index 

meddat <- read_csv("./MSFS-estimates_full-3x2000.csv",
    show_col_types=FALSE)


df.media <- df.precision %>%
    left_join(meddat,
              by = c("year"= "year",
                  "cow" = "abbr"))

## Bring group-year change info into the
## group-country-year df.precision + media info

df.precision2 <- df.media %>%
    left_join(df.yearsum,
              by=c("groupID"= "groupID",
                  "year"= "year"))

dat <-df.precision2 %>%
    group_by(groupID, country_id, year) %>%
    mutate(gcyid = cur_group_id()) ## creates a grouping id for group-country

## Fixed effects by group
## for change from previous year's ratio,
## given precision and media freedom
## BUT taking absolute value of the previous year change
## because otherwise the [-1, 1] scale washes out any possible signal:

## SE Grouped just at group level:
## b/c group-country-year is the unit of analysis
## so it's weird to group at that:

mod2B<- plm(propdif.L1 ~ mean.loc.prec +
            mean.clarity + mean.time.prec +  MSF,
            model=c("random"),## random effects
            effect="time", ## time fixed effects
            index=c("groupID"),
            data=dat)

df <- tidy(mod2B)
ci95 <- confint(mod2B, level=0.95) %>% 
  data.frame() %>%
  rename("conf.low95" = "X2.5..",
         "conf.high95" = "X97.5..")

ci90 <- confint(mod2B, level=0.9) %>% 
  data.frame() %>%
  rename("conf.low90" = "X5..",
         "conf.high90" = "X95..")

results <- bind_cols(df, 
                     ci95, 
                     ci90) %>%
    rename(Variable = term,
           Coefficient = estimate,
           SE = std.error) %>%
           filter(Variable != "(Intercept)")

gg1 <- ggplot(results, 
       aes(x = Variable, y = Coefficient)) +
        geom_hline(yintercept = 0, 
                   colour = gray(1/2), lty = 2) +
        geom_point(aes(x = Variable, 
                    y = Coefficient)) + 
        geom_linerange(aes(x = Variable, 
                     ymin = conf.low90,
                     ymax = conf.high90),
                   lwd = 1) +
        geom_linerange(aes(x = Variable, 
                     ymin = conf.low95,
                     ymax = conf.high95),
                   lwd = 1/2) + 
    ggtitle("Outcome: Yearly Proportion Changes",
            subtitle= "S.E. Clustered by Group") +
    coord_flip() +
    theme_bw()

gg1 ##Manuscript Fig
ggsave(gg1,
       file="lmAbsPropDifL1.pdf")

## Another view:
## Look at years since change and precision.
## Which asks if it is the case that
## presentation is more stable when information is
## less precise
## This is a zero inflated negative binomial since
## have 0s from no changes & also zeros from year after deltas

cols <- c("counter", "mean.loc.prec",
          "mean.clarity","mean.time.prec",
          "MSF", "groupID")

## Need to remove NA for clustered errors:
dat2 <- na.omit(dat[,cols]) ## 2298 x 6

mod3 <- zeroinfl(counter ~ mean.loc.prec +
            mean.clarity + mean.time.prec +  MSF,
                 data=dat2,
                 dist="negbin")

mod3ci <- coeftest(mod3,
                   vcov = vcovCL(mod3, cluster = dat2$groupID))

df <- tidy(mod3ci) ## then exoponentiate the coef:

ci95 <- confint(mod3ci, level=0.95) %>% 
    data.frame() %>%
    rename("conf.low95" = "X2.5..",
           "conf.high95" = "X97.5..")

ci90 <- confint(mod3ci, level=0.9) %>% 
  data.frame() %>%
  rename("conf.low90" = "X5..",
         "conf.high90" = "X95..")

results <- bind_cols(df, 
                     ci95, 
                     ci90) %>%
    rename(Variable = term,
           Coefficient = estimate,
           SE = std.error) %>%
           filter(Variable != "(Intercept)")


gg2 <- ggplot(results, 
       aes(x = Variable, y = Coefficient)) +
        geom_hline(yintercept = 0, 
                   colour = gray(1/2), lty = 2) +
        geom_point(aes(x = Variable, 
                    y = Coefficient)) + 
        geom_linerange(aes(x = Variable, 
                     ymin = conf.low90,
                     ymax = conf.high90),
                   lwd = 1) +
        geom_linerange(aes(x = Variable, 
                     ymin = conf.low95,
                     ymax = conf.high95),
                   lwd = 1/2) + 
    ggtitle("Outcome: Years Since Change Period",
            subtitle="S.E. Clustered by Group ID; Model Neg Bin") +
    coord_flip() +
    theme_bw()

gg2 ## Manuscript Appendix Fig
ggsave(gg2,
       file="negBinomMedia.pdf")


```

## Appendix AQAP Topic Comparison

The following code presents Table One of the Appendix, which presents a yearly summary for alternate model specifications for AQAP. 

## Appendix AQAP Topic Comparison

The following code presents Table One of the Appendix.

```{r altSpecs, echo=FALSE}
source("implementAltPKKAQAP.R") 
```