---
title: "STC_Replication_All_Log"
author: "Margaret J. Foster"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Replication Log for Foster (2024) Subject to Change

This Markdown script calls the component files needed to produce the Subject to Change text-based change metric. This script demonstrates the operation and output of the scripts that produce the component data and generates logs of each script. 

The component scripts themselves are loquacious, with comments and summaries throughout. I include these to help any user get a sense of how each component fits together and what is happening under the hood.

To replication just the production of the plots and figures in the paper (without generating the data), see `ReplicationRLog.Rmd` and the resulting `ReplicationRLog.pdf` R markdown output.

For a replication (and log) of the application, see `STC_STATA_Rep_All.do`

## Libraries and version control
```{r libaries, message=FALSE}
setwd("~/Dropbox/TransformationEmpiricalModels/Replication/dataverse_files_2/")

library("groundhog")

packs <- c("ggplot2", "ggridges", "readxl", 
           "stargazer", 'tidyverse',
           "quanteda", "stm", "stringi", 
           "ggrepel")

## The important version to be aware of is that
## quanteda had a major change between versions 3 and 4
## The results replicate with quanteda V3, which was how it was developed

groundhog_day_deps <- "2023-11-21" ##
groundhog.library(c("MASS", "Matrix", "RcppArmadillo", 
                    "fastmatch", "RcppParallel","Rcpp",
                    "SnowballC", "stopwords"),
                  groundhog_day_deps,
                  tolerate.R.version='4.3.3')

groundhog_day <- "2024-02-01" ##
groundhog.library(c("ggplot2", "ggridges", "readxl", "stargazer", 'tidyverse',
                    "quanteda", "stm", "stringi", "ggrepel", "ggplot2",
                    "ggridges", "countrycode", "sandwich", "lmtest", "plm",
                    "broom", "corrplot", "haven", 'pscl', "broom"),
                  groundhog_day,
                  ignore.deps = c("MASS", "Matrix", "RcppArmadillo", 
                                  "fastmatch", "RcppParallel",
                                  "SnowballC", "stopwords", 
                                  'Rcpp', 'ISOcodes'),
                  tolerate.R.version='4.3.3')
```

## Data Procesing

```{r measurement, echo=TRUE, message=FALSE}
rmarkdown::render("./01measurementFullDataTinyThreshRep.R")
```

## Estimating Change

Runtime: Approximately 5 minutes on 32G Apple M1 2021 Macbook Pro

```{r transform, echo=TRUE, message=FALSE}
rmarkdown::render("./02tinyThreshTransformVarRep.R")
```


```{r estimate, echo=TRUE, message=FALSE}
rmarkdown::render("./03analysisFullDataTinyThreshRep.R")
```

## Prepare the terminaion and recurrance application

```{r termination, echo=TRUE, message=FALSE}
rmarkdown::render("./04nsPrepTerminationRep.R")
```

```{r replication, echo=TRUE, message=FALSE}
rmarkdown::render("./04nsPrepRecurrance.R")
```

## Highlighting group plots

Produce the spotlight plots, along with qualitative views into the data. 

```{r groupplots, echo=TRUE, message=FALSE}
rmarkdown::render("./analysisGroupPlotsRep.R")
```


Analysis of the effects of location precision on the change variable: 
```{r precision, echo=TRUE, message=FALSE}
rmarkdown::render("./03ClocationPrecisionRep.R")
```
## Analysis of sensitivity to sparseness

Note that "RobustnessPanel.R" requires several hours to run because it does a gridsearch of the entire data 
generating process for 9 different inclusion thresholds. Each round take about 45 minutes to run.

```{r threshold, echo=TRUE, message=FALSE}
rmarkdown::render("./RobustnessPanel.R")
```


```{r altspec, echo=TRUE, message=FALSE}
rmarkdown::render("./checkAlternateSpecTiny.R")
```

## Analysis of effects of changing the K

```{r altspec_k, echo=TRUE, message=FALSE}
rmarkdown::render("./implementAltPKKAQAP.R")
```